Reproducible Research Practices and Barriers to Reproducible Research in Geography: Insights from a Survey

### 2023-01-11 docs/manuscript/manuscript.tex
Update results

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Statistical Methods}
We conduct two statistical analyses of the survey response. 
First, we use descriptive statistical summaries to address our four questions about how geographic researchers define reproducibility, their familiarity and experience with reproducible research practice, and the barriers to reproducibility they perceive in the discipline. 
To assess the familiarity of geographic researchers with reproducible and open science research practices, we created a single aggregate variable by recoding and then summing these measures. 
This procedure produced a single aggregate variable with a minimum value of 0 and a maximum value of 5.

@@

Second, we conduct an analysis of the experience of geographic researchers who have attempted reproductions of prior work. 
We examine what motivates geographic researchers to attempt to reproduce another study and how successful researcher attempting reproductions were at recreating existing results. 
We also investigate why

@@

%%%%%%%%%%%
\subsubsection*{Definition of Reproducibility}
\begin{itemize}
    \item Self-reported definition (Q6) analysis: Qualitative analysis that will present a typology of definitions by combination of the Q,Q,M and M,P,NS,H splits that match on the 8 category coding of the provided definitions. 
    \item Interpretations (Q8) and Importance (Q17) of reproductions: Develop a split that distinguishes between Qs that focus on epistemology Q8a+Q8b+Q8f+17a, as these provide the most direct information about how a respondent processes the evidence provided by a reproduction; and Qs that focus on reproducibility as a quality of a study Q8e+Q8c+17c+17e+17f. We will explore how these question groups crosstab with the typologies we draw from Q6. Initial assumption is that many will support reproduction as a study characteristic or label, and less will link it with epistomological function. Examine by subfields and methods, which we expect to align with typologies from Q6. 
    \item Importance of reproducibility (Q17) - Reproducibility was/wasn't seen as important for other open science goals - error reduction (17b), effort duplication (17d), scientific communication (17g, 17h), training (17i, 8d).
    \item Reproducibility Estimate (Q13) - \textcolor{red}{What is the state of the summaries on this dimension?}
\end{itemize}

%%%%%%%%%%%
\subsubsection*{Familiarity with Reproduciblity Practices}

%%%%%%%%%%%
\subsubsection*{Frequency of Reproduciblity Practices}
Q9 will feather in to contextualize the measure

%%%%%%%%%%%
\subsubsection*{Barriers to Reproduction}
Discussion of details from Q14

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Actual Reproductions}
Start with the outline of what the population is here because not all respondents answered these questions. Start with descriptives that show this sub-sample of respondents. Summary discussion of Q10-Q12.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Statistical Methods}
We conduct two statistical analyses of the survey response. 
First, we used descriptive statistical summaries of the participant response to address our four questions about how geographic researchers define reproducibility, their familiarity and experience with reproducible research practice, and the barriers to reproducibility they perceive in the discipline.
For each question, we created a single variable that aggregates a participant's response across a subset of survey questions related to that issue.

We measured each participant's definition of reproducibility relative to the definition provided by the \citet{NASEM2019}. 
Before being provided a standardized definition, each participant was asked to provide their own definition of reproducibility. 
We coded these text responses along four dimensions of data, procedure, result, and context similarity.  
To assess researcher familiarity with reproducible practices, we created a single variable, \textit{Familiarity}, that counts the number of practices a researcher was 'somewhat' or 'very' familiar with.
To assess researcher experience with reproducible practices, we created a single variable, \textit{Experience}, that counts the number of practices a researcher use 'most of the time' or 'always' when conducting their own research. 
Our \textit{Familiarity} and \textit{Experience} variables both range from 0-5. 
We similarly created a single measure, \textit{Barriers} that counts the number of factors a researcher believe 'frequently' or 'occasionally' contributed to a lack of reproducibility. 
This \textit{Barriers} variable ranges from 0-12.

@@

Second, we conduct an analysis of the experience of geographic researchers who have attempted reproductions of prior work. 
A total of \textit{n}=102 of the authors we contacted reported attempting to reproduce a prior study. 
We examine what motivates geographic researchers to attempt to reproduce another study and how successful researcher attempting reproductions were at recreating existing results. 
We also investigate why researchers were unable to reproduce results.

@@

%%%%%%%%%%%
\subsubsection*{Definition of Reproducibility}
Coded definitions are relative to the NASEM definition. The NASEM state SAME data, procedures, and results and implies SAME context because data is not recollected. 
\begin{itemize}
    \item Self-reported definition (Q6) analysis: Qualitative analysis that will present a typology of definitions by combination of the Q,Q,M and M,P,NS,H splits that match on the 8 category coding of the provided definitions. 
    \item Interpretations (Q8) and Importance (Q17) of reproductions: Develop a split that distinguishes between Qs that focus on epistemology Q8a+Q8b+Q8f+17a, as these provide the most direct information about how a respondent processes the evidence provided by a reproduction; and Qs that focus on reproducibility as a quality of a study Q8e+Q8c+17c+17e+17f. We will explore how these question groups crosstab with the typologies we draw from Q6. Initial assumption is that many will support reproduction as a study characteristic or label, and less will link it with epistomological function. Examine by subfields and methods, which we expect to align with typologies from Q6. 
    \item Importance of reproducibility (Q17) - Reproducibility was/wasn't seen as important for other open science goals - error reduction (17b), effort duplication (17d), scientific communication (17g, 17h), training (17i, 8d).
    \item Reproducibility Estimate (Q13) - \textcolor{red}{What is the state of the summaries on this dimension?}
\end{itemize}

%%%%%%%%%%%
\subsubsection*{Reproducible Research Practices and Barriers to Reproducibility}
This will be a discussion of how subfields differ on the specific questions used to create the aggregate variables presented above. 
The purpose is to enrich the overall picture by identifying differences within the aggregate measures.
\begin{itemize}
    \item Use Q9 to contextualize the frequency measure.
    \item Use details from Q14 to enrich the discussion of barriers
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Actual Reproductions}
A total of \textit{n}=102 of the authors we contacted reported attempting to reproduce a prior study.

Start with the outline of what the population is here because not all respondents answered these questions. Start with descriptives that show this sub-sample of respondents. Summary discussion of Q10-Q12.
